\chapter{Acknowledgements}
\label{chap:acknowledgements}

This thesis represents four years of research carried out at the University of Newcastle, surrounded by exceptional people without whom I would not have been able to complete such a big project.

My thanks go to my supervisors Peter Andras and Jennifer Hallinan for their support an encouragement. Peter with his unbelievable knowledge of just about everything, calmly and patiently explaining whatever I asked him and Jennifer making sure that if and when I wrote anything down, there were enough commas and apostrophes in the right places. I also have to thank Wolfgang Stein and everybody in his lab who taught me the dissection and electrophysiological techniques and were always available, over the years, to answer questions and give advice.

I have a great deal of appreciation for my office colleagues Sarah Crabbe, Kanida Sinmai and Frances Hutchings. They had to put up with my quirks, my proof reading and my moods. 

I would like to thank my children, Leonetta and Stuart who have had to live in an ever increasing untidy house with the promise that when this thesis is submitted, both them and the house will get more of my attention.

I have to thank my friend Carol Booth who has always, since the day we met, been there to support and motivate me.

Few things are impossible with the support of one's family. So I have to thank my mother and the rest of my family. My mother for all the baby sitting when I had to go to conferences and the rest of the family for always telling me that they believe in me.

Lastly I would like to give an honourable mention to PhD comics which, although distracting at times, did remind me that I was not the only one feeling totally overwhelmed and unproductive at times. 

This research was funded with a scholarship from the Newcastle University School of Computing Science.

