\chapter{Publications}
\label{chap:Publications}

The following publications and posters were produced by, or in conjunction with, the author during her PhD candidacy. The list also includes publications that are currently being prepared.

\section{Journal Paper:}
Dan Bai, Andrew C. Benniston, Sophie Clift, Ulrich Baisch, \textbf{Jannetta Steyn}, Nicola Everitt, Peter Andras, \textit{Low molecular weight Neutral Boron Dipyrromethene (Bodipy) dyads for fluorescence-based neural imaging}, Journal of Molecular Structure, Volumes 1065–1066, 22 May 2014, Pages 10-15, ISSN 0022-2860,
\url{http://dx.doi.org/10.1016/j.molstruc.2014.02.026.}

\section{Posters:}
J. S. Steyn$^{1}$, W. Stein$^{2}$, C. Staedele$^{2}$, P. Andras$^{1}$; $^{1}$Sch. of Computing Sci., Newcastle Univ., Newcastle Upon Tyne, United Kingdom; $^{2}$Neurobio., Ulm Univ., Ulm, Germany, \textit{Are the activities of crustacean STG neurons of the same class equivalent under neuromodulatory conditions ?}, Neuroscience 2011, Washington DC.

J. S. Steyn, P. Andras; Sch. of Computing Sci., Newcastle Univ., Newcastle Upon Tyne, United Kingdom, \textit{Investigation of the role of dopamine in the re-organisation of functional neural circuits in the context of learning a conditional behavioural association}, Neuroscience 2012, New Orleans.

J. S. Steyn$^{1}$, C. A. Harris$^{2,3}$, G. Kemenes$^{3}$, P. Andras$^{1}$; 
$^{1}$Sch. of Computing Sci., Newcastle Univ., Newcastle Upon Tyne, United Kingdom; $^{2}$Circuit Dynamics and Connectivity Unit, NINDS, NIH, Maryland, MD; $^{3}$Sussex Univ., Sussex, United Kingdom, \textit{Multi-electrode array recording of the crab stomatogastric ganglion}, Neuroscience 2013, San Diego.

J. S. Steyn$^{1}$,$^{2}$, T. Alderson$^{1}$, P. Andras$^{1}$,$^{2}$,$^{3}$; $^{1}$Sch. of Computing Sci., Newcastle Univ., Newcastle Upon Tyne, United Kingdom; $^{2}$Inst. of Neurosci., Newcastle upon Tyne, United Kingdom; $^{3}$Sch. of Computing and Mathematics, Keele Univ., Keele, United Kingdom, \textit{Computational modelling and analysis of the impact of dopamine on the crustacean pyloric rhythm circuit}, Neuroscience 2014, Washington DC.

\section{Technical Report}
 CS-TR-1477, August 2015: Jannetta S. Steyn$^{1}$ and Peter Andras$^{2}$, $^{1}$School of Computing Science, Newcastle University, $^{2}$School of Computing and Mathematics, Keele University, \textit{Analysis of the dynamics of temporal relationships of neural activities using imaging data.}

\section{In preparation:}
Jannetta S. Steyn$^{1}$ and Peter Andras$^{2}$, $^{1}$School of Computing Science, Newcastle University, $^{2}$School of Computing and Mathematics, Keele University, \textit{Analysis of the dynamics of temporal relationships of neural activities using imaging data.}

